---
title: "6 - Reporting"
author: "Tony the Tiger"
output: html_document
---


```{r setup, include=FALSE}
# This is an R code chunk - include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
# setup is the name of the code chunk
# you can only use a name once for the code chunk name

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```
***
Example One:  
```{r}
# This is a code chunk with no name and no specified options
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

diamondCutCount

```
***
Example Two:  
```{r echoFalse, echo = FALSE}
# This is a code chunk with the name echoFalse and echo option = FALSE
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

diamondCutCount

```
***
Example Three:  
```{r evalFalse, eval = FALSE}
# This is a code chunk with the name evalFalse and eval option = FALSE
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

diamondCutCount

```
  
***
Example Four:  
```{r includeFalse, include = FALSE}
# This is a code chunk with the name includeFalse and include option = FALSE
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

diamondCutCount

```

***
Example Five:    
```{r graphics1, echo = TRUE}
# Dislaying grapics with echo = TRUE
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

ggplot(diamondCutCount, aes(x=cut, weight=n)) +
  geom_bar()

```
  
***
Example Six:  
```{r graphics2, echo = FALSE}
# Dislaying grapics with echo = FALSE
diamondCutCount <- diamonds %>% 
  group_by(cut) %>% 
  count()

ggplot(diamondCutCount, aes(x=cut, weight=n)) +
  geom_bar()

```
***

# Header 1
## Header 2
### Header 3
#### Header 4
##### Header 5
###### Header 6


End a line with two spaces to start a new paragraph.  
*italics* and _italics_  
**bold** and __bold__  
superscript^2^  
~~strikethrough~~  
[link](www.rstudio.com)  

horizontal rule (or slide break):    

***      

* unordered list  
* item 2  
 + sub-item 1  
 + sub-item 2  

1. ordered list  
2. item 2  
  + sub-item 1  
  + sub-item 2   
 
 
Table Header | Second Header  
------------- | -------------  
Table Cell | Cell 2
Cell 3 | Cell 4


Inline Code:  
Two to the power of eight = `r 2^8`


***
Interactive Plots Example:  
```{r interactive, echo = FALSE, include = FALSE}
# Need to add 'runtime: "shiny"' to YAML header
# Change include to TRUE

# selectInput(
#   'cuts', label = 'Select diamond cut:',
#   choices = unique(diamonds$cut)
# )
# 
# renderPlot({
#   
#   ggplot((diamonds %>% 
#            filter(cut == input$cuts)), aes(x=price)) +
#   geom_histogram()
#   
# })


```


